\documentclass{beamer}
\usepackage{graphicx}
\usepackage{hyperref}

\title{Ghost Dodgers}
\author{WE\_Crafters}
\institute{Disha Singla, Krishita Garg, Yasaswini Devi}
\date{\today}

\begin{document}

\frame{\titlepage}

\begin{frame}{Objective}
    \begin{itemize}
        \item Recreate the Pac-Man game with different themes.
        \item Understand the fundamentals of game development.
        \item Explore the features offered by Pygame.
    \end{itemize}
\end{frame}

\begin{frame}{Tech Stack}
    \begin{itemize}
        \item Pygame
        \item HTML
        \item CSS
        \item JavaScript
        \item LaTeX
    \end{itemize}
\end{frame}

\begin{frame}{Journey}
    \begin{enumerate}
        \item Initial planning and dividing the tasks.
        \item Setting up the prerequisites.
        \item Navigating through the challenges posed.
        \item Connecting the individual parts into a working piece of code.
        \item Adjusting the code according to team mates' suggestions.
        \item Debugging throughout all these steps.
    \end{enumerate}
\end{frame}

\begin{frame}{Learnings}
    \begin{itemize}
        \item Working with Pygame.
        \item Utilizing graphics in Pygame.
        \item Understanding the fundamentals of game development.
        \item Coordinating and working with team mates.
        \item Modularizing the code.
        \item Debugging.
    \end{itemize}
\end{frame}

\begin{frame}{Explorations}
    \begin{itemize}
        \item A* algorithm for pathfinding.
        \item Backtracking algorithm for maze generation.
    \end{itemize}
\end{frame}

\begin{frame}{Future Aspects}
    \begin{itemize}
        \item Implementing a 1v1 player mode.
        \item Making the ghost behavior more unpredictable.
        \item Including special artifacts.
        \item Incorporating more themes.
    \end{itemize}
\end{frame}

\begin{frame}{Conclusion}
    \begin{itemize}
        \item Successfully recreated the Pac-Man game with various themes.
        \item Gained a deeper understanding of game development.
        \item Explored advanced algorithms for enhancing gameplay.
        \item Identified future improvements and extensions.
    \end{itemize}
\end{frame}

\begin{frame}{Q\&A}
    \begin{center}
        \Huge{Questions?}
    \end{center}
\end{frame}

\end{document}
